\vspace{-2.5em} Optimizing angular diSPIM measurements\vspace{-1em}

### 2019-02-28 notes/2019-01-28-angular-optimize/report/report.tex
Patrick's angular diSPIM optimization edits.

We can rewrite the mapping in Eq. \eqref{eq:cc} in an object-space spherical
harmonic basis as
\begin{align}
  g(\sd, \pp) = \sum_{\ell m}H_\ell^m(\sd, \pp)F_\ell^m,\label{eq:fwdsh}
\end{align}
where $F_\ell^m$ is the angular dipole spectrum given by 
\begin{align}
  F_\ell^m = \int_{\mbb{S}^2}d\so\, f(\so)Y_\ell^{m*}(\so),
\end{align}
and $H_\ell^m(\sd, \pp)$ is the kernel in this basis given by
\begin{align}
  H_\ell^m(\sd, \pp) &= \sum_{\ell' m'}\sum_{\ell'' m''}(-1)^m G_{\ell,\ell',\ell''}^{-m,m',m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\sd),\label{eq:triple4}\\
    H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
    H_{\ell''}^{m'',\text{det}}(\sd) &\propto \frac{Y_{\ell''}^{m''*}(\sd)}{1 - \cos\alpha}\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right].\label{eq:dipdet}
\end{align}
with the Gaunt coefficients given by 
\begin{align}
  G_{\ell,\ell',\ell''}^{m,m',m''} = \ints{2}d\so\, Y_\ell^{m}(\so)Y_{\ell'}^{m'}(\so)Y_{\ell''}^{m''}(\so).
\end{align}

It's useful to compare Eq. \eqref{eq:fwd} to Eq. \eqref{eq:fwdsh}---in a delta
function basis we need to compute an angular integral, while in the object-space
spherical harmonics basis the kernel has a finite number of terms so we can
compute it exactly.

@@

\section{Sampling schemes}
We can write the sampling operation as a continuous-to-discrete Hilbert space
operator $\mc{D}_w$
\begin{align}
  \mb{g}_d = \mc{D}_w\mb{g}_c = \mc{D}_w\mc{H}_{cc}\mb{f}_c. 
\end{align}
We can write the sampling operation in a delta function basis as
\begin{align}
  g_m = \int_{\mbb{S}^2}d\sd\int_{\mbb{S}^1}d\pp\, w_m(\sd,\pp)g(\sd,\pp).
\end{align}
where $g_m$ is the $m$th discrete measurement and $w_m(\sd,\pp)$ is the $m$th
sampling aperture. For now we will restrict ourselves to delta-function sampling
apertures
\begin{align}
  w_m(\sd,\pp) = \delta(\mh{s}_{d,m} - \sd)\delta(\mh{p}_{m} - \pp),
\end{align}
where $\mh{s}_{d,m}$ and $\mh{p}_{m}$ are the $m$th sampling points. This
restriction means that we will leave the polarizer setting and tilt angle fixed
during each volume acquisition. We could consider scanning the polarizer
setting and tilt angle in the future for faster acquisitions, but I think these
sampling schemes will always decrease ``angular SNR''.

@@

Next, we constrain the polarizer sampling points $\mh{p}_m$. We introduce a
variable $\mh{s}_{e,m}$ to denote the excitation optical axis for the $m$th
measurement. This variable does not affect the forward model (we've formulated
in terms of $\pp$ only on the excitation side), but it will allow us to
conveniently constrain $\pp$. First, we constrain the excitation optical axis to
be perpendicular to the detection optical axis
\begin{align}
  \mh{s}_{e,m} \cdot \mh{s}_{d,m} = 0.
\end{align}
This is a fairly loose constraint, but it ensures that the light sheet is in
focus across the field of view.

@@

Earlier we mainly used the Schatten 2-norm of the continuous-discrete imaging
operator---the root sum of squares of the singular values---as the objective
function. This objective function resulted in useful designs, but the last
singular value was usually small which led us to optimizing the condition
number. We can interpret the Schatten 2-norm designs as the ``learn as much as
we can about all parameters'' designs and the condition number designs as the
``no parameter left behind'' designs.

@@

In the \textbf{top right} subfigure we show an set of single direction
reconstructions with the given design. We start by creating a uniformly oriented
phantom for each of the 250 directions in the positive octant of the sphere
indicated by \textcolor{green}{green} dots. Next, we simulate the imaging
process, simulate Poisson noise with SNR = 20, reconstruct the phantom, then
find maximum of the reconstructed ODF. We mark each reconstructed maximum with a
\textcolor{red}{red} dot and connect each phantom/reconstruction pair with a
black line.

>>>>

We can rewrite the mapping in Eq. \eqref{eq:cc} in an object-space spherical
harmonic basis as
\begin{align}
  g(\sd, \pp) = \sum_{\ell m}H_\ell^m(\sd, \pp)F_\ell^m,\label{eq:fwdsh}
\end{align}
where $F_\ell^m$ is the angular dipole spectrum given by 
\begin{align}
  F_\ell^m = \int_{\mbb{S}^2}d\so\, f(\so)Y_\ell^{m*}(\so),
\end{align}
and $H_\ell^m(\sd, \pp)$ is the kernel in this basis given by
\begin{align}
  H_\ell^m(\sd, \pp) &= \sum_{\ell' m'}\sum_{\ell'' m''}(-1)^m G_{\ell,\ell',\ell''}^{-m,m',m''}H_{\ell'}^{m',\text{exc}}(\pp)H_{\ell''}^{m'',\text{det}}(\sd),\label{eq:triple4}\\
    H_{\ell'}^{m',\text{exc}}(\pp) &\propto Y_{\ell'}^{m'*}(\pp)\left[\delta_{0\ell'} + \frac{2}{5}\delta_{2,\ell'}\right],\label{eq:dipexc}\\
    H_{\ell''}^{m'',\text{det}}(\sd) &\propto \frac{Y_{\ell''}^{m''*}(\sd)}{1 - \cos\alpha}\left[(1 - \sqrt{\cos\alpha})\delta_{0,\ell''} + \left(\frac{2}{5} + \frac{1}{10}\sqrt{\cos\alpha}(-7+3\cos\alpha)\right)\delta_{2,\ell''}\right],\label{eq:dipdet}
\end{align}
with the Gaunt coefficients given by 
\begin{align}
  G_{\ell,\ell',\ell''}^{m,m',m''} = \ints{2}d\so\, Y_\ell^{m}(\so)Y_{\ell'}^{m'}(\so)Y_{\ell''}^{m''}(\so).
\end{align}

It's useful to compare Eq. \eqref{eq:fwd} to Eq. \eqref{eq:fwdsh}---in a delta
function basis we need to compute a continuous angular integral (in general this
requires an approximate Riemann sum), while in the object-space spherical
harmonics basis the kernel has a finite number of terms so we can compute it
exactly.

@@

\section{Sampling schemes}
We can write the sampling operation as a continuous-to-discrete Hilbert space
operator $\mc{D}_w$
\begin{align}
  \mb{g}_d = \mc{D}_w\mb{g}_c = \mc{D}_w\mc{H}_{cc}\mb{f}_c. 
\end{align}
We can write the sampling operation in a delta function basis as
\begin{align}
  g_m = \int_{\mbb{S}^2}d\sd\int_{\mbb{S}^1}d\pp\, w_m(\sd,\pp)g(\sd,\pp).
\end{align}
where $g_m$ is the $m$th discrete measurement and $w_m(\sd,\pp)$ is the $m$th
sampling aperture. For now we will restrict ourselves to delta-function sampling
apertures
\begin{align}
  w_m(\sd,\pp) = \delta(\mh{s}_{d,m} - \sd)\delta(\mh{p}_{m} - \pp),
\end{align}
where $\mh{s}_{d,m}$ and $\mh{p}_{m}$ are the $m$th sampling points. This
restriction means that we will leave the polarizer setting and tilt angle fixed
during each volume acquisition. We could consider scanning the polarizer setting
and tilt angle while acquiring data in the future for faster imaging, but I
think these sampling schemes will always decrease ``angular SNR''.

@@

Next, we constrain the polarizer sampling points $\mh{p}_m$. We introduce a
variable $\mh{s}_{e,m}$ to denote the excitation optical axis for the $m$th
measurement. This variable does not affect the forward model (we've formulated
in terms of $\pp$ only on the excitation side), but it will allow us to
conveniently constrain $\pp$. First, we constrain the excitation optical axis to
be perpendicular to the detection optical axis
\begin{align}
  \mh{s}_{e,m} \cdot \mh{s}_{d,m} = 0.
\end{align}
This constraint ensures that the light sheet is in focus across the field of
view.

@@

Earlier we mainly used the Schatten 2-norm of the continuous-discrete imaging
operator---the root sum of squares of the singular values---as the objective
function. This objective function resulted in useful designs, but the last
singular value was usually small which led us to optimizing the condition number
instead. We can interpret the Schatten 2-norm designs as the ``learn as much as
we can about all parameters'' designs and the condition number designs as the
``no parameter left behind'' designs.

@@

In the \textbf{top right} subfigure we show a set of single direction
reconstructions with the given design. We start by creating a uniformly oriented
phantom for each of the 250 directions in the positive octant of the sphere
indicated by \textcolor{green}{green} dots. Next, we simulate the imaging
process, simulate Poisson noise with SNR = 20, reconstruct the phantom, then
find maximum of the reconstructed ODF. We mark each reconstructed maximum with a
\textcolor{red}{red} dot and connect each phantom/reconstruction pair with a
black line.
